\section{Definitions and Observations}
\label{sec:Definitions and Observations}
\subsection{Graphs and Paths}
\label{sub:Graphs and Paths}
We start by writing out some basic definitions from graph theory.
\begin{definition}
  A \textbf{graph} $\bm{G} = (G, N)$ is a tuple where the first element $G$ is a set representing the nodes in the graph, while the second element $N$ is a set representing the edges (neighbours).
  $N$ is usually represented as a subset of $G \times G$ where $(u,v) \in N$ iff there is an edge from node $u$ to node $v$ in the graph.
\end{definition}
Another way to think of $N$ is as a function $N: G \rightarrow \mathcal{P}(G)$ where $N(x)$ returns the set of all out-neighbours of $x$.
\begin{definition}
  A \textbf{path} is a sequence of nodes $(x_0, x_1, x_2, \dots, x_n)$ from the graph in which all nodes (except possibly the first and last) are distinct, such that for any two consequtive nodes $x_i,x_{i+1}$, we have that $(x_i, x_{i+1}) \in N$.
  In this case we say that there is a path from $x_0$ to $x_n$.
\end{definition}
For every $x$ in the graph, we have the unique empty path $(x)$ of length 0.
This path is distinct from the loop $(x,x)$.
\subsection{Proof-specific relations}
\label{sub:Proof-specific relations}
\begin{definition}
  Given a node $x$ and a collection of nodes $Y$, we have that \bm{$E(x,Y)$} holds iff $x$ has outgoing edges targeting exactly the nodes in $Y$\todo{This definition has to be changed}.
\end{definition}
\begin{definition}
  Given two nodes $x,y$ we have that \bm{$P(x,y)$} holds iff there exists a path between $x$ and $y$.
  We will use \bm{$P_o$} and \bm{$P_e$} to denote paths of odd and even lengths, respectively.
\end{definition}
The text will sometimes use the notion of \textit{path lengths}.  This will not refer to the actual length of the path, but whether or not it is of even or odd length.
\begin{definition}
  A path $P(x_0,x_n)$ is \textbf{fully trimmed} (denoted \bm{$P^f(x_0,x_n)$}) if no nodes in the path branches off elsewhere.
  This means that for every pair of consecutive nodes $x_i,x_{i+1}$ in the path, we need that $E(x_i,\{ x_{i+1} \})$.
\end{definition}
\begin{definition}
  A path $P(x_0,x_n)$ is \textbf{evenly trimmed} (denoted \bm{$P^e(x_0,x_n)$}) if every evenly indexed node is non-branching.
  Said differently, for every \textit{even} $i < n$ we need $E(x_i,\{x_{i+1}\})$ to hold.
\end{definition}
\begin{definition}
  A path $P(x_0,x_n)$ is \textbf{oddly trimmed} (denoted \bm{$P^o(x_0,x_n)$}) if for every \textit{odd} $i < n$, $E(x_i,\{x_{i+1}\})$ holds.
\end{definition}
We will usually denote paths with both length and trim in combination, i.e. $\peo(x,y)$.
This is solely to simplify the proofs and is nothing more than an abbreviation for $P^e(x,y) \wedge P_o(x,y)$, meaning an evenly trimmed odd path from $x$ to $y$.
\begin{definition}
  There is a \textbf{vel} between two nodes $x$ and $y$ (denoted \bm{$V(x,y)$}) if and only if there exists a node $c$ such that $P^o(x,c)$ and $P^o(y,c)$ and the sum of the two path lengths is odd. In formal terms we have that
  \[
  V(x,y) \Leftrightarrow (\poo(x,c) \wedge \poe(y,c)) \vee (\poe(x,c) \wedge \poo(y,c))
  \]
\end{definition}
By introducing a bit more notation, we will be able to write this formal defintion of a vel in a nicer way.
By abstracting over the actual lengths and trims of paths we can make statements like:
\[P_x(a,b) \wedge P_x(b,c) \Rightarrow P_e(a,c) \quad\text{where}\quad x \in \{e,o\}\]
This lets us argue about paths of equal length (even or odd) in one statement instead of explicitly describing both cases.
The statements above tells us that the concatenation of two paths of equal length (even or odd) results in an even path\todo{Rewrite section. Use P+E examples instead of P+P}.

Similarly, we can argue about paths of different lengths by introducing $\overline{x}$ as a piece of notation such that $\overline{o} = e$ and $\overline{e} = o$.
We can now make statements like \[P_x(a,b) \wedge P_{\overline{x}}(b,c) \Rightarrow P_o(a,c)\] telling us that concatenating two paths of different lengths (even or odd) results in an odd path.
We are now able to write our definition of a vel in a nice, shorter way\todo{Does the definition below need an existencial quantifier?}:
\[
V(a,b) \Leftrightarrow \exists x(\pox(a,c) \wedge \ponx(b,c))
\]
\subsection{Immediate observations}
\label{sub:Immediate observations}
\begin{lemma}
  $P^f(x,y) \Rightarrow P^o(x,y) \wedge P^e(x,y)$
\end{lemma}
 This implication should be easy to accept; a fully trimmed path has branching restrictions on all its nodes, both the odd and the even ones.
 It is thus both oddly and evenly trimmed.

 The opposite implication is actually also true, allthough not as obvious, since it would seem that $P^o(x,y)$ could refer to a path partly disjoint from $P^e(x,y)$ and there would thus be no single path both oddly and evenly trimmed.
 We will later show that this can't actually be the case.
\begin{lemma}
  $P_e(x,x)$ for every $x \in G_v$
\end{lemma}
This will denote the empty path mentioned earlier.
The path is even simply because 0 is even.
\begin{lemma}
  $E(x,\{ y \}) \Rightarrow P^f_o(x,y)$
\end{lemma}
An edge is another trivial example of a path.
The path is fully trimmed since $x$ does not branch off.
In the more general case of $E(x,Y)$, we have that $P^o_o(x,y)$ holds for every $y \in Y$.
\begin{lemma}
  $\poo(x,y) \Rightarrow V(x,y)$
\end{lemma}
A vel needs two paths of even and odd length, respectively.
Since the even path can be empty, we get that any odd path is a vel by itself.
\section{Path composition}
\label{sec:Path composition}
Suppose we have two paths; one from $a$ to $b$ and one from $b$ to $c$.
We can now obtain a path going from $a$ to $c$ by first traversing from $a$ to $b$ using the first path, then traversing from $b$ to $c$ using the second path.
This operation is called \textbf{path composition} and the resulting path is called a \textbf{composite path}.
We can use our notation to make a statement about path composition:
\[
P(a,b) \wedge P(b,c) \Rightarrow P(a,c)
\]
In this case, we say that $P(a,b)$ is composed with $P(b,c)$.

Let's extend this statement in order to describe the change in length.
We observe that when composing two even -- or two odd -- paths, the resulting path will always be even, but when composing one path of even length with one of odd length, the resulting path will be odd.
Introducing length to the equation thus gives us two cases:
\begin{align*}
  P_x(a,b) \wedge P_x(b,c) \Rightarrow P_e(a,c)\\
  P_x(a,b) \wedge P_{\overline{x}}(b,c) \Rightarrow P_o(a,c)
\end{align*}
The next step will be to extend these statements even further to also capture the behavior of trimming under composition.
In order to do this, let's first make some observations:

First, unlike with the length property, we do not have any guarantee that a composite path has a trim at all.
We might need to set certain restrictions to our two original paths in order to get a properly trimmed (either evenly or oddly) path as a result after composition.  It should at least be obvious that both original paths should be trimmed in some way.

Secondly, no matter what path you compose a trimmed path with, the resulting composite path will always be of the same trim, if trimmed at all.
This means that given a path $P^e(a,b)$ and a path $P(b,c)$, the composite path from $a$ to $c$ will never be oddly trimmed. Equivalently, a composition of $P^o(a,b)$ and $P(b,c)$ will never result in $P^e(a,c)$.

Now, let's look at some examples.
The below figure shows instances of the four possible combinations of trims and lengths of a path.
All nodes $x$ and edges $(x,y)$ such that $E(x,\{ y\})$ are depicted in red\todo{Should I avoid using colors in the paper?} and will from here on be referred to as \textit{non-branching} nodes and \textit{unique} edges, respectively\todo{Overkill?}.
\[
  \item \begin{tikzpicture}
    [
    point/.style={thick,circle,draw,inner sep=0pt,minimum size=2mm},
    trimmed/.style={thick,draw=red},
    untrimmed/.style={thick,draw=black}
    ]
    \node (0) at (0,0) [point,label=left:$\poo\quad$] ] {};
    \node (1) at (1,0) [point,trimmed] {};
    \node (2) at (2,0) [point] {};
    \node (3) at (3,0) [point,trimmed] {};
    \node (4) at (4,0) [point] {};
    \node (5) at (5,0) [point] {};
    \draw [-latex,untrimmed] (0) to (1);
    \draw [-latex,trimmed] (1) to (2);
    \draw [-latex,untrimmed] (2) to (3);
    \draw [-latex,trimmed] (3) to (4);
    \draw [-latex,untrimmed] (4) to (5);

    \node (0) at (0,1) [point,trimmed,label=left:$\peo\quad$] ] {};
    \node (1) at (1,1) [point] {};
    \node (2) at (2,1) [point,trimmed] {};
    \node (3) at (3,1) [point] {};
    \node (4) at (4,1) [point,trimmed] {};
    \node (5) at (5,1) [point] {};
    \draw [-latex,trimmed] (0) to (1);
    \draw [-latex,untrimmed] (1) to (2);
    \draw [-latex,trimmed] (2) to (3);
    \draw [-latex,untrimmed] (3) to (4);
    \draw [-latex,trimmed] (4) to (5);

    \node (0) at (0,2) [point,label=left:$\poe\quad$] ] {};
    \node (1) at (1,2) [point,trimmed] {};
    \node (2) at (2,2) [point] {};
    \node (3) at (3,2) [point,trimmed] {};
    \node (4) at (4,2) [point] {};
    \draw [-latex,untrimmed] (0) to (1);
    \draw [-latex,trimmed] (1) to (2);
    \draw [-latex,untrimmed] (2) to (3);
    \draw [-latex,trimmed] (3) to (4);

    \node (0) at (0,3) [point,trimmed,label=left:$\pee\quad$] ] {};
    \node (1) at (1,3) [point] {};
    \node (2) at (2,3) [point,trimmed] {};
    \node (3) at (3,3) [point] {};
    \node (4) at (4,3) [point] {};
    \draw [-latex,trimmed] (0) to (1);
    \draw [-latex,untrimmed] (1) to (2);
    \draw [-latex,trimmed] (2) to (3);
    \draw [-latex,untrimmed] (3) to (4);
  \end{tikzpicture}
\]
In the above figure, we have examples of the four possible combinations of trim and length of a path.  The trimmed nodes and their respective unique out-edges are depicted in red.
